### 2016-08-26 notions.tex
cheers

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.6}{.35}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathrm{err}\gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.}
\label{fig:correctness}
\end{figure}

@@

\jnote{OK, from here on I specialize to set-representation data structures\ldots}
The one-wayness definition (see
Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
sets. \jnote{I got rid of the weaker definition, since it seems unnatural to me.}
A set $S$ is chosen from this distribution, and a representation
$(M,\pubaux,\privaux)$ of that set is computed.
In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), the attacker is given $M, \pubaux$;
in a second experiment (${\bf Exp}^{\rm null}_{\Pi,\distr{}{}}$), it is not.
In both cases, the attacker is given
access to an oracle via which it can
issue queries and obtain the corresponding responses.
For a given $\distr{}{}$ and $A$, we define the advantage measure
$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{{\bf Exp}^{\rm null}_{\Pi,\distr{}{}}(A)=1} \right|$.
We track the
time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.

@@

\medskip
\experimentv{${\bf Exp}^{\rm null}_{\Pi, \distr{}{}}(A)$} \\
$S \getsr \distr{}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}()$\\
if $z \in S$ then return 1\\
return 0\\
%\medskip
%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$z \getsr A^{\TestOracle}(\pubaux)$\\
%if $z \in S$ then Return 1\\
%Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
return~$a$
}
}
\caption{Experiments for a ``one-wayness'' style privacy
  definition.}
\label{fig:privacy-ow}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{${\bf Exp}^{\rm ss\mbox{-}rep\mbox{-}1}_{\Pi}(A)$}\\
$S \gets A()$ \\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(M,\pubaux)$\\

\medskip
\experimentv{${\bf Exp}^{\rm ss\mbox{-}rep\mbox{-}0}_{\Pi, {\sf leak}}(A, \calS)$}\\
$S \gets A()$\\
$(M,\pubaux) \getsr \calS({\sf info}(S))$ \\
return $A(M,\pubaux)$\\
%\medskip
%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$z \getsr A^{\TestOracle}(\pubaux)$\\
%if $z \in S$ then Return 1\\
%Return 0\\
}
%
{}
}
\caption{Experiments for a ``semantic-security'' style privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

>>>>

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathrm{err}\gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.}
\label{fig:correctness}
\end{figure}

@@

\jnote{OK, from here on I specialize to set-representation data structures\ldots}
The one-wayness definition (see
Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
sets. \jnote{I got rid of the weaker definition, since it seems unnatural to me.}
A set $S$ is chosen from this distribution, and a representation
$(M,\pubaux,\privaux)$ of that set is computed.
In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), the attacker is given $M, \pubaux$;
in a second experiment ($\ExpPrivNull{\Pi,\distr{}{}}{}$), it is not.
In both cases, the attacker is given
access to an oracle via which it can
issue queries and obtain the corresponding responses.
For a given $\distr{}{}$ and $A$, we define the advantage measure
$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{A}=1} \right|$.
We track the
time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.

@@

\medskip
\experimentv{$\ExpPrivNull{\Pi, \distr{}{}}{A}$} \\
$S \getsr \distr{}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\emptystring,\emptystring)$\\
if $z \in S$ then return 1\\
return 0\\
%\medskip
%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$z \getsr A^{\TestOracle}(\pubaux)$\\
%if $z \in S$ then Return 1\\
%Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
return~$a$
}
}
\caption{Experiments for a ``one-wayness'' style privacy
  definition.}
\label{fig:privacy-ow}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
$S \gets A()$ \\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
return $A(M,\pubaux)$\\

\medskip
\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \calS}$}\\
$S \gets A()$\\
$(M,\pubaux) \getsr \calS({\sf leak}(S))$ \\
return $A(M,\pubaux)$\\
%\medskip
%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$z \getsr A^{\TestOracle}(\pubaux)$\\
%if $z \in S$ then Return 1\\
%Return 0\\
}
%
{}
}
\caption{Experiments for a ``semantic-security'' style privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}
